---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tidbits

The goal of tidbits is to package up some utility functions that have proven 
useful in multiple data analysis projects and teaching, so they can be 
properly documented and more easily deployed. Including `autoread()` function
which wraps readers for a wide variety of data formats so the same script can
run on different files without editing the file-loading code.

## Installation

You can install tidbits from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bokov/tidbits")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidbits);
# Read data from the NAACCR website
dat00 <- autoread('https://www.naaccr.org/wp-content/uploads/2017/02/naaccr_cina_2009_2013_stage.sas7bdat');
# Build an automatic data dictionary
dct0 <- tblinfo(dat00)

```

[![Travis-CI Build Status](https://travis-ci.org/bokov/tidbits.svg?branch=integration)](https://travis-ci.org/bokov/tidbits)
[![Coverage Status](https://img.shields.io/codecov/c/github/bokov/tidbits/integration.svg)](https://codecov.io/github/bokov/tidbits?branch=integration)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/bokov/tidbits?branch=integration&svg=true)](https://ci.appveyor.com/project/bokov/tidbits)
